TADCompare: an R package for differential analysis and characterization of Topologically Associated Domains

### 2019-09-24 manuscript/manuscript.Rmd
Describe p-values

## Coherence of all phenotypes significantly differs from random

@@

>>>>

@@

## Coherence of most phenotypes significantly differs from random

Given the wide range of phenotype-specific coherence estimates, a natural question is whether they significantly different from random coherence. We assesses the significance of coherence estimates using permutation test (see Methods), individually for each PPI database. Permutation p-values obtained using Biogrid and STRING filtered databases were higly correlated (PCC = 0.71, Supplementary Figure S1), as would be expected for high-quality PPIs. Permutation p-values using STRING databases were predominantly significant (p-value < 0.001) due to the large number of PPIs that enable phenotype-specific networks to be consistently different from random. Permutation p-values inversely correlated with coherence estimates (average PCC = -0.23), as would be expected for less coherent networks that resemble random networks. This dependency was especially pronounced for database-specific estimates, e.g., Biogrid coherence and p-value estimates correlated with PCC = -0.73 (STRING filtered PCC = -0.51, Supplementary Figure S1). These observations confirmed consistent coherence and p-value estimates when using different PPI databases.

The majority of phenotype-specific networks (~85%) were significantly coherent (STRING filtered p-value < 0.001, Supplementary Table S3). Among less significant phenotypes were "White blood cell count" (p-value = 0.102) and other blood count-related phenotypes, "Corneal astigmatism" (p-value = 0.05), "Major depressive disorder" (p-value = 0.03). When using Biogrid databases, "Educational attainment", "Myopia (pathological)", "Celiac disease" were among the non-significant phenotypes (p-values 0.29, 0.20,0.16, respectively). Interestingly, "Schizophrenia" network, despite being among the least coherent, was consistently significantly different from random (p-value < 0.001). Overall, significance estimation of coherence supports our observation that phenotype-specific networks in "Intelligence" and "Psychiatric disease" categories generally have low coherence. These results further confirm our ability to identify phenotype-specific networks with low, non-significant coherence.
